### 2014-12-16 3-algorithms.tex
As of Sep 30, 2014 diff --git a/0-abstract.tex b/0-abstract.tex new file mode 100644 index 0000000..642c9e6 --- /dev/null +++ b/0-abstract.tex @@ -0,0 +1,18 @@ + +Blogs are one of the most prominent means of communication on the web. +Their content, interconnections and influence constitute a unique +socio-technical artefact of our times which needs to be preserved. +The BlogForever project has established best practices and developed an +innovative system to harvest, preserve, manage and reuse blog content. +This paper presents the latest developments of the blog crawler which +is a key compo

\section{Algorithms}
\label{algorithms}

This section explains in detail the algorithms we developed to extract blog post articles as well as its variations for extracting authors, dates and comments. Our approach uses blog specific characteristics to build \emph{extraction rules} which are applicable throughout a blog. Our focus is on minimising the algorithmic complexity while keeping our approach simple and generic.

@@

Extracting metadata and content from HTML documents is a challenging task. Standards and format recommendations have been around for quite some time, strictly specifying how HTML documents should be organised~\cite{w3c2014}. For instance the \code{<h1></h1>} tags have to contain the highest-level heading of the page and must not appear more than once per page~\cite{w3c2002}. More recently, specifications such as microdata~\cite{whatwg2014} define ways to embed semantic information and metadata inside HTML documents, but these still suffer from very low usage: estimated to be used in less than 0.5\% of websites~\cite{andrewrogers2014}. In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise the structure of pages, and more than 95\% of pages do not pass HTML validation~\cite{brianwilson2008}. Under such circumstances, relying on HTML structure to extract content from web pages is not viable and other techniques need to be employed.

\Anotecontent{observations}{Our experiments on a large dataset of blogs showed that failing tests were either due to a violation of one of these observations, or to an insufficient amount of text in posts.}

Having blogs as our target websites, we made the following observations which play a central role in the extraction process\Anote{observations}:
\begin{enumerate}[label={(\alph*)}]
  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the latest posts of a blog,
  \item\label{similarhtmlAssum} Posts of the same blog share a similar HTML structure.
\end{enumerate}
Web feeds usually contain about 20 blog posts~\cite{oita2010}, often less than the total number of posts in blogs. Consequently, in order to effectively archive the entire content of a blog, it is necessary to download and process pages beyond the ones referenced in the web feed.

@@

% per blog procedure, related work
To extract content from blog posts, we proceed by building \emph{extraction rules} from the data given in the blog's web feed. The idea is to use a set of \emph{training data}, pairs of HTML pages and target content, to build an extraction rule capable of locating the target content on each HTML page.

% input from observations.
Observation~\ref{havefeedAssum} allows the crawler to obtain input for the extraction rule generation algorithm: each web feed entry contains a link to the corresponding web page as well as the blog post article (either abstract or full text), its title, authors and publication date. We call these fields \emph{targets} as they constitute the data our crawler aims to extract. Observation~\ref{similarhtmlAssum} guarantees the existence of an appropriate extraction rule, as well as its applicability to all posts of the blog.

@@

Unsurprisingly, the choice of \code{ScoreFunction} greatly influences the running time and precision of the extraction process. When targeting articles, extraction rule scores are computed with a string similarity function comparing the extracted strings with the target strings. We chose the Sørensen–Dice coefficient similarity~\cite{dice1945}, which is, to the best of our knowledge, the only string similarity algorithm fulfilling the following criteria:

\begin{enumerate}
  \item\label{wordorderProp} Has low sensitivity to word ordering,
  \item\label{lengthProp} Has low sensitivity to length variations,
  \item\label{linearProp} Runs in linear time.
\end{enumerate}

Properties \ref{wordorderProp} and \ref{lengthProp} are essential when dealing with cases where the blog's web feed only contains an abstract or a subset of the entire post article. \autoref{similarityTable} gives examples to illustrate how these two properties hold for the Sørensen–Dice coefficient similarity but do not for \emph{edit distance} based similarities such as the Levenshtein~\cite{levenshtein1966} similarity.

\similarityTable

The Sørensen–Dice coefficient similarity algorithm operates by first building sets of pairs of adjacent characters, also knows as \emph{bigrams}, and then applying the \emph{quotient of similarity} formula:

@@

While very intuitive, the original idea of first generating extraction rules and then picking these best rules prevents us from effectively reusing previously computed bigrams (set of pairs of adjacent characters). For instance, when evaluating the extraction rule for the HTML root node, \autoref{extractionAlgo} will obtain the complete string of the page and pass it to the \coderef{similarityAlgo} function. At this point, the information on where the string could be split into substrings with already computed bigrams is not accessible, and the bigrams of the page have to be computed by linearly traversing the entire string. To overcome this limitation and implement \emph{memoization} over the bigrams computations, \autoref{linearAlgo} uses a post-order traversal of the HTML tree and computes node bigrams from their children bigrams. This way, we avoid serializing HTML subtrees for each bigrams computation and have the guarantee that each character of the HTML page will be read at most once during the bigrams computation.

@@

\begin{itemize}
  \item Rules returning fewer HTML nodes than the number of comments on the feed are filtered out with a zero~score,
  \item The scores of the remaining rules are computed with the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ has weight equal to \coderef{similarityAlgo}\code{(}\emph{u, v}\code{)}.
\end{itemize}
Our crawler executes this algorithm on each post with an overflow on its comment feed, thus supporting blogs with multiple commenting engines. The comment content is extracted first, allowing us to narrow down the initial filtering by fixing a target number of comments.

Regarding time complexity, computing the \emph{tree distance} of each node of a graph to a single reference node can be done in linear time, and multiplying the number of targets by a constant factor does not affect the asymptotic computational complexity. Computing scores of comment extraction rules requires a more expensive algorithm. However, this is compensated by the fact that the proportion of candidates left, after filtering out rules not returning enough results, is very low in practice. Analogous reformulations to the one done with \autoref{linearAlgo} can be straightforwardly applied on each \code{ScoreFunction} in order to minimize the time spent in \coderef{similarityAlgo}.

>>>>

\section{Algorithms}
\label{algorithms}
We propose a new set of algorithms to extract blog post articles as well 
as variations for extracting authors, dates and comments. We start with 
our motivation to use blog specific characteristics, followed by our 
approach to build \emph{extraction rules} which are applicable throughout 
a blog. Our focus is on minimising the algorithmic complexity while 
keeping our approach simple and generic.

@@

Extracting metadata and content from HTML documents is a challenging task 
because standards and format recommendations suffer from very low usage. 
W3C has been publishing web standards and format recommendations for 
quite some time~\cite{w3c2014}. For instance, according to the W3C 
HTML guidelines, the \code{<h1></h1>} tags have to contain the 
highest-level heading of the page and must not appear more than 
once per page~\cite{w3c2002}. More recently, specifications such 
as microdata~\cite{whatwg2014} define ways to embed semantic information 
and metadata inside HTML documents, but these still suffer from 
very low usage: estimated to be used in less than 0.5\% of 
websites~\cite{andrewrogers2014}. In fact, the majority of websites rely 
on the generic \code{<span></span>} and \code{<div></div>} container 
elements with custom \code{id} or \code{class} attributes to organise 
the structure of pages, and more than 95\% of pages do not pass HTML 
validation~\cite{brianwilson2008}. Under such circumstances, relying 
on HTML structure to extract content from web pages is not viable and 
other techniques need to be employed.

Having blogs as our target websites, we made the following observations 
which play a central role in the extraction process:

\begin{enumerate}
\item\label{havefeedAssum} 
Blogs provide web feeds: structured and standardized views of the latest 
posts of a blog.
\item\label{similarhtmlAssum} 
Posts of the same blog share a similar HTML structure.
\end{enumerate}

Web feeds usually contain about 20 blog posts~\cite{oita2010}, 
often less than the total number of posts in blogs. Consequently, to 
effectively archive the entire content of a blog, it is necessary to 
download and process pages beyond the ones referenced in the web feed.

@@

% per blog procedure, related work
To extract content from blog posts, we proceed by building 
\emph{extraction rules} from the data given in the blog's web feed. 
The idea is to use a set of \emph{training data}, pairs of HTML pages 
and target content, which are used to build an extraction rule capable 
of locating the target content on each HTML page.

% input from observations.
Observation (\ref{havefeedAssum}) allows the crawler to obtain input for 
the extraction rule generation algorithm: each web feed entry contains a 
link to the corresponding web page as well as blog post article (either 
abstract or full text), its title, authors and publication date. We call 
these fields \emph{targets} as they constitute the data our crawler aims 
to extract. Observation (\ref{similarhtmlAssum}) guarantees the existence 
of an appropriate extraction rule, as well as its applicability to all 
posts of the blog.

@@

Unsurprisingly, the choice of \code{ScoreFunction} greatly influences 
the running time and precision of the extraction process. When targeting 
articles, extraction rule scores are computed with a string similarity 
function comparing the extracted strings with the target strings. 
We chose the Sorensen–Dice coefficient similarity~\cite{dice1945}, 
which is, to the best of our knowledge, the only string similarity 
algorithm fulfilling the following criteria:

\begin{itemize}
\item\label{wordorderProp} Has low sensitivity to word ordering,
\item\label{lengthProp} Has low sensitivity to length variations,
\item\label{linearProp} Runs in linear time.
\end{itemize}

Properties \ref{wordorderProp} and \ref{lengthProp} are essential when 
dealing with cases where the blog's web feed only contains an abstract 
or a subset of the entire post article. \autoref{similarityTable} 
gives examples to illustrate how these two properties hold for the 
Sorensen–Dice coefficient similarity but do not for \emph{edit distance} 
based similarities such as the Levenshtein~\cite{levenshtein1966} 
similarity.

\begin{table}
\tbl{Examples of string similarities.}
{\begin{tabular}{@{}llcc@{}} \toprule
        \textbf{string1} & \textbf{string2} & \textbf{Sorensen-Dice} & \textbf{Levenshtein} \\
    \midrule
    \stringliteral{Scheme Scala} & \stringliteral{Scala Scheme}
    & 90\% & 50\% \\
    \stringliteral{Rachid} & \stringliteral{Richard}
    & 18\% & 61\% \\
    \stringliteral{Rachid} & \stringliteral{Amy, Rachid and all their friends}
    & 29\% & 31\% \\ \hline
\end{tabular}}
\label{similarityTable}
\end{table}

The Sorensen–Dice coefficient similarity algorithm operates by 
first building sets of pairs of adjacent characters, also known as 
\emph{bigrams}, and then applying the \emph{quotient of similarity} formula:

@@

While very intuitive, the original idea of first generating extraction 
rules and then picking these best rules prevents us from effectively 
reusing previously computed $N$-grams (sets of adjacent characters). 
For instance, when evaluating the extraction rule for the HTML root node, 
\autoref{extractionAlgo} will obtain the complete string of the page 
and pass it to the \coderef{similarityAlgo} function. At this point, 
the information on where the string could be split into substrings with 
already computed $N$-grams is not accessible, and the $N$-grams of 
the page have to be computed by linearly traversing the entire string. 
To overcome this limitation and implement \emph{memoization} over the 
$N$-gram computations, \autoref{linearAlgo} uses a post-order traversal 
of the HTML tree and computes node $N$-grams from their children 
$N$-grams. This way, we avoid serializing HTML subtrees for each 
$N$-gram computation and have the guarantee that each character of the 
HTML page will be read at most once during the $N$-gram computation.

An interesting question is what is the optimal $N$ for $N$-gram 
computation. To answer this question, we conduct some simple experiments. 
Using sample blog post excerpts and full texts, we calculate the string 
similarity between each excerpt and full text. For instance, using a blog 
post full text and associated text excerpt from the popular blog TechCrunch
as presented in Table \ref{table:techcrunch}, the text similarity results
(Table \ref{table:similarity-n-values}) using different $N$ values support
the selection of bigrams ($N$=2).

\begin{table}
\tbl{TechCrunch blog post example.}
{\begin{tabular}{@{}p{12cm}@{}} \toprule
\emph{Blog post text} \\ \hline
Apple has a new version of iOS 8 out, just a short time after the 
initial launch of the software. The update, 8.0.1, includes a number of 
fixes, but most notably (and listed first), it addressed the bug that 
prevented HealthKit apps from being available at launch. It also zaps 
some bugs with third-party keyboards, which should make them remain the 
default option until a user switches to another, which has been a sore 
spot for fans of the new external software keyboard options.

Unfortunately, installing the iOS 8.0.1 update revealed that despite 
Apple’s promised fixes, it actually completely disables cellular service 
and Touch ID on many devices, though some iPhone 5s and older model 
owners report no issues. The bottom line is that you should definitely 
NOT install this update, at least until an updated version appears, 
at which time we’ll let you know it’s safe to go ahead.

As you can see in the image below, Apple is also addressing an issue that 
blocked some photos from appearing in Photo Library, fixing reliability 
concerns around Reachability on iPhone 6 and 6 Plus (which brings the top 
of the screen down when you double touch the Home button), zapping bugs 
that cause unexpected data use when communicating via SMS or MMS, and 
improving the “Ask to Buy” feature for Family Sharing, specifically 
around in-app purchases, in addition to other minor bugs.\\ \hline

\emph{Weblog post text abstract from RSS} \\ \hline
Apple has a new version of iOS 8 out, just a short time after the 
initial launch of the software. The update, 8.0.1, includes a number of 
fixes, but most notably (and listed first), it addressed the bug that 
prevented HealthKit apps from being available at launch. It also zaps... \\ \hline
\end{tabular}}
\label{table:techcrunch}
\end{table}

\begin{table}
\tbl{Blog post excerpt and full text similarity using different $N$ values.}
{\begin{tabular}{@{}lccc@{}} \toprule
        \emph{$N$} & \emph{2} & \emph{3} & \emph{4} \\ \hline
Similarity & 0.7817 & 0.6680 & 0.6212 \\ \hline
\end{tabular}}
\label{table:similarity-n-values}
\end{table}

@@

\begin{itemize}
\item 
Rules returning fewer HTML nodes than the number of comments on the feed 
are filtered out with a zero~score,
\item 
The scores of the remaining rules are computed with the value of the 
\emph{maximum weighted matching} in the \emph{complete bipartite graph} 
$G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, 
$V$ is the set of target comment fields from the web feed (such as 
comment authors) and $E(u, v)$ has weight equal to 
\coderef{similarityAlgo}\code{(}\emph{u, v}\code{)}.
\end{itemize}

Regarding time complexity, computing the \emph{tree distance} of each 
node of a graph to a single reference node can be done in linear time, 
and multiplying the number of targets by a constant factor does not 
affect the asymptotic computational complexity. Computing scores of 
comment extraction rules requires a more expensive algorithm. However, 
this is compensated by the fact that the proportion of candidates left, 
after filtering out rules not returning enough results, is very low in 
practice. Analogous reformulations to the one done with 
\autoref{linearAlgo} can be straightforwardly applied on each 
\code{ScoreFunction} to minimize the time spent in 
\coderef{similarityAlgo}.

### 2014-12-16 5-evaluation.tex
As of Sep 30, 2014 diff --git a/0-abstract.tex b/0-abstract.tex new file mode 100644 index 0000000..642c9e6 --- /dev/null +++ b/0-abstract.tex @@ -0,0 +1,18 @@ + +Blogs are one of the most prominent means of communication on the web. +Their content, interconnections and influence constitute a unique +socio-technical artefact of our times which needs to be preserved. +The BlogForever project has established best practices and developed an +innovative system to harvest, preserve, manage and reuse blog content. +This paper presents the latest developments of the blog crawler which +is a key compo

Our evaluation is articulated in two parts. First, we compare the article extraction procedure presented in \autoref{algorithms} with three open-source projects capable of extracting articles and titles from web pages. The comparison will show that our blog-targeted solution has better performance both in terms of success rate and running time. Second, a discussion is held regarding the different solutions available to archive data beyond what is available in the HTML source code. Extraction of authors, dates and comments is not part of this evaluation because of the lack of publicly available competing projects and reference data sets.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extraction success rates}
To evaluate article and title extraction from blog posts we compare our approach to three open source projects: Readability\footnote{\url{https://github.com/gfxmonk/python-readability}}, Boilerpipe~\cite{kohlschuetter2010} and Goose\footnote{\url{https://github.com/GravityLabs/goose}}, which are implemented in JavaScript, Java and Scala respectively. These projects are more generic than our blog-specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of the same blog (observations \ref{havefeedAssum} and \ref{similarhtmlAssum}). \autoref{precisionTable} shows the extraction success rates for article and title on a test sample of 2300 blog posts from 230 blogs obtained from the Spinn3r dataset~\cite{burton2011}.

\precisionTable

On our test dataset, \autoref{extractionAlgo} outperformed the competition by 4.9\% on article extraction and 10.1\% on title extraction. It is important to stress that Readability, Boilerpipe and Goose rely on generic techniques such as word density, paragraph clustering and heuristics on HTML tagging conventions, which are designed to work for any type of web page. On the contrary, our algorithm is only suitable for pages with associated web feeds, as these provide the reference data used to build extraction rules. Therefore, results shown in \autoref{precisionTable} should not be interpreted as a general quality evaluation of the different projects, but simply as evidence that our approach is more suitable when working with blogs.

@@

In addition to the quality of the extracted data we also evaluated the running time of the extraction procedure. The main point of interest is the ability of the extraction procedure to scale as the number of posts in the processed blog increases. This corresponds to the evaluation of a \emph{NewCrawl} task, which is in charge of harvesting all published content on a blog.

\autoref{runningtime} shows the cumulated time spent for each article extraction procedure (this excludes common tasks such as downloading pages and storing results) as a function of the number of blog posts processed. We used the Quantum Diaries\footnote{\url{http://www.quantumdiaries.org}} blog for this experiment.

Data presented in this graph was obtained by taking the arithmetic mean over 10 measurements. These results are believed to be significant given that standard deviations are of the order of 2 milliseconds.

\input{runningtimeFigure.tex}

As illustrated in \autoref{runningtime}, our approach spends the majority of its total running time between the initialisation and the processing of the first blog post. This initial increase of about 0.4 seconds corresponds to cost of executing \autoref{linearAlgo} to compute extraction rule for articles. As already mentioned, this consists of computing the \emph{best extraction rule} of each page referenced by the web feed and picking the most appropriate one. Once we have this extraction rule, processing subsequent blog posts only requires parsing and applying the rule, which takes about 3 milliseconds and are barely visible on the scale of \autoref{runningtime}. The other evaluated solutions do not function this way: each blog post is processed as new and independent input, leading to approximately linear running times.

The vertical dashed line at 15 processed blog posts represents a suitable point of comparison of processing time per blog post. Indeed, as the web feed of our test blog contains 15 blog posts, the extraction rule computation performed by our approach includes the cost of entirely processing these 15 entries. That being said, comparing raw performance of algorithms implemented in different programming languages is not very informative given the high variation of running times observed across programming languages~\cite{hundt2011}.

>>>>

Our evaluation is articulated in two parts. First, we compare the 
article extraction procedure presented in \autoref{algorithms} with 
three open-source projects capable of extracting articles and titles 
from web pages. The comparison will show that our weblog-targeted solution 
has better performance both in terms of success rate and running time. 
Second, a discussion is held regarding the different solutions available 
to archive data beyond what is available in the HTML source code. 
Extraction of authors, dates and comments is not part of this evaluation 
because of the lack of publicly available competing projects and 
reference data sets.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extraction success rates}

To evaluate article and title extraction from weblog posts 
we compare our approach to three open source projects: 
Readability\footnote{\url{https://github.com/gfxmonk/python-readability}}, 
Boilerpipe~\cite{kohlschuetter2010} and Goose\footnote{\url{https://github.com/GravityLabs/goose}}, 
which are implemented in JavaScript, Java and Scala respectively. 
These projects are more generic than our blog-specific approach in the 
sense that they are able to identify and extract data directly from HTML 
source code, and do not make use of web feeds or structural similarities 
between pages of the same weblog (observations (\ref{havefeedAssum}) and 
(\ref{similarhtmlAssum})). Table \ref{table:evaluation-performance} shows the extraction 
success rates for article and title on a test sample of 2300 posts 
from 230 weblogs obtained from the Spinn3r dataset~\cite{burton2011}.

\begin{table}
\tbl{Extraction success rates for different algorithms.}
{\begin{tabular}{@{}lcccc@{}} \toprule
		\textbf{Target} & \textbf{Our~approach} & \textbf{Readability} & \textbf{Boilerpipe} & \textbf{Goose} \\ \hline
    Article & 93.0\% & 88.1\% & 79.3\% & 79.2\% \\
    Title   & 95.0\% & 74.0\% & N/A    & 84.9\% \\ \hline
\end{tabular}}
\label{table:evaluation-performance}
\end{table}

On our test dataset, \autoref{extractionAlgo} outperformed the 
competition by 4.9\% on article extraction and 10.1\% on title 
extraction. It is important to stress that Readability, Boilerpipe 
and Goose rely on generic techniques such as word density, paragraph 
clustering and heuristics on HTML tagging conventions, which are designed 
to work for any type of web page. On the contrary, our algorithm is 
only suitable for pages with associated web feeds, as these provide the 
reference data used to build extraction rules. Therefore, results shown 
in Table \ref{table:evaluation-performance} should not be interpreted as a general 
quality evaluation of the different projects, but simply as evidence 
that our approach is more suitable when working with weblogs.

@@

In addition to the quality of the extracted data we also evaluated the 
running time of the extraction procedure. The main point of interest is 
the ability of the extraction procedure to scale as the number of posts 
in the processed weblog increases. This corresponds to the evaluation of 
a \emph{NewCrawl} task, which is in charge of harvesting all published 
content on a weblog.

Figure \ref{runningtime} shows the cumulated time spent for each article 
extraction procedure (this excludes common tasks such as downloading 
pages and storing results) as a function of the number of weblog posts 
processed. We used the Quantum Diaries\footnote{\url{http://www.quantumdiaries.org}} 
blog for this experiment. Data presented in this graph was obtained
by taking the arithmetic mean over 10 measurements. These results are
believed to be significant given that standard deviations are of
the order of 2 milliseconds.

\begin{figure*}[!hbt]
\centering
\label{runningtime}
\input{main-gnuplottex-fig1.tex}
\end{figure*}

As illustrated in \autoref{runningtime}, our approach spends the majority 
of its total running time between the initialisation the processing 
of the first weblog post. This initial increase of about 0.4 seconds 
corresponds to cost of executing \autoref{linearAlgo} to compute 
extraction rule for articles. As already mentioned, this consists 
in computing the \emph{best extraction rule} of each pages references 
by the web feed and picking the one functioning best on these pages. 
Once we have this extraction rule, processing subsequent weblog posts only 
requires parsing and applying the rule, which takes about 3 milliseconds 
and are barely visible on the scale of \autoref{runningtime}. The other 
evaluated solutions do not function this way: each weblog post is processed 
as new and independent input, leading to approximately linear running 
times.

The vertical dashed line at 15 processed weblog posts represents a suitable 
point of comparison of processing time per post. Indeed, as the 
web feed of our test weblog contains 15 posts, the extraction rule 
computation performed by our approach include the cost of entirely 
processing these 15 entries. That being said, comparing raw performance 
of algorithms implemented in different programming languages is not very 
informative given the high variations of running times observed across 
programming languages~\cite{hundt2011}.

### 2014-12-16 runningtimeFigure.tex
As of Sep 30, 2014 diff --git a/0-abstract.tex b/0-abstract.tex new file mode 100644 index 0000000..642c9e6 --- /dev/null +++ b/0-abstract.tex @@ -0,0 +1,18 @@ + +Blogs are one of the most prominent means of communication on the web. +Their content, interconnections and influence constitute a unique +socio-technical artefact of our times which needs to be preserved. +The BlogForever project has established best practices and developed an +innovative system to harvest, preserve, manage and reuse blog content. +This paper presents the latest developments of the blog crawler which +is a key compo

\begin{figure}[t]
  \vspace{-12pt}
  \hspace{-34pt}
  \begin{gnuplot}% nop
    set terminal epslatex color
    set size 0.75
    set size ratio 0.618

    set ylabel 'Cumulated running time (sec.)' offset 1.3
    set xlabel 'Processed blog posts'

    set yrange [0:44]
    set xrange [0:65]
    set key invert

@@

    plot 'data/runningtime.txt'\
       u 0:1 smooth cumulative w lines linewidth 3 title 'Our approach',\
    '' u 0:4 smooth cumulative w lines linewidth 4 title 'Readability',\
    '' u 0:2 smooth cumulative w lines linewidth 4 title 'Boilerpipe',\
    '' u 0:3 smooth cumulative w lines linewidth 4 title 'Goose'
  \end{gnuplot}
  \vspace{-18pt}
  \caption{Running time of article extraction.}
  \label{runningtime}
\end{figure}

>>>>

\begin{figure}[ht]
  \capstart
  \refstepcounter{figure}
  \label{runningtime}
  \vspace{-12pt}
  \hspace{-34pt}
  \begin{gnuplot}% nop
    set terminal epslatex color
    set size 0.76
    set size ratio 0.618

    set title 'Figure \arabic{figure}: Running time of articles extraction.'
    set ylabel 'Cumulated running time (sec.)' offset 1.3
    set xlabel 'Processed blog posts'

    set yrange [0:44]
    set xrange [0:65]

@@

    plot 'data/runningtime.txt'\
       u 0:1 smooth cumulative w lines linewidth 3 title 'Our approach',\
    '' u 0:4 smooth cumulative w lines linewidth 4 title 'Readability',\
    '' u 0:2 smooth cumulative w lines linewidth 4 title 'Boilerpipe',\
    '' u 0:3 smooth cumulative w lines linewidth 4 title 'Goose'
  \end{gnuplot}
  \vspace{-12pt}
\end{figure}
